\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-10 paper.qmd
Add 2D layouts of PBMC and Mouse data

a2 + a1 +
  plot_annotation(tag_levels = 'a') +
  plot_layout(ncol = 3) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

@@

## To draw with AIC
aic_plot_param <- ggplot(MSE_df_umap |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                                                                         y = total_error,
                                                                         color = param
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_color_discrete_qualitative() +
  ylab("AIC") +
  xlab("Total number of bins")
## Effective number of bins along x-axis

mse_plot_param_training <- ggplot(MSE_df_umap |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                               y = total_mse,
                               color = param
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_color_discrete_qualitative() +
  ylab("MSE") +
  xlab("Total number of bins")

mse_plot_param_test <- ggplot(MSE_df_umap |> dplyr::filter(data_type == "test"), aes(x = number_of_bins,
                                                                                             y = total_mse,
                                                                                             color = param
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_color_discrete_qualitative() +
  ylab("MSE") +
  xlab("Total number of bins")

@@

```{r}
#| warning: false
#| echo: false
# InstallData("pbmc3k")
# data("pbmc3k.final")
# 
# data_pca <- as.data.frame(pbmc3k.final@reductions$pca@cell.embeddings)
# names(data_pca) <- paste0(rep("PC", ncol(data_pca)), 1:ncol(data_pca))
# 
# data_pca_with_label <- bind_cols(pbmc3k.final@reductions$pca@cell.embeddings, pbmc3k.final@meta.data$seurat_clusters)
# names(data_pca_with_label)[ncol(pbmc3k.final@reductions$pca@cell.embeddings) + 1] <- "cluster_label"
# 
# levels(data_pca_with_label$cluster_label) <- c("Naive CD4 T", "Memory CD4 T", "CD14+ Mono", "B", "CD8 T", "FCGR3A+ Mono", "NK", "DC", "Platelet")

data_pca_with_label <- readRDS(file = paste0(here::here(), "/data/pbmc_with_label.rds"))

data_pca <- data_pca_with_label %>%
  select(-cluster_label)
```

```{r}
#| warning: false
#| echo: false
# eigs <- pbmc3k.final@reductions$pca@stdev^2 ## To calculate eigen values
# 
# summary_pca <- rbind(
#   SD = sqrt(eigs),
#   Proportion = eigs/sum(eigs),
#   Cumulative = cumsum(eigs)/sum(eigs))
# 
# var_explained_df <- data.frame(PC = paste0("PC", 1:ncol(pbmc3k.final@reductions$pca@cell.embeddings)),
#                                var_explained = (pbmc3k.final@reductions$pca@stdev)^2/sum((pbmc3k.final@reductions$pca@stdev)^2))

var_explained_df <- readRDS(file = paste0(here::here(), "/data/pbmc_var_explained.rds"))

pbmc_var_explain <- var_explained_df %>%
    ggplot(aes(x = PC,y = var_explained, group = 1))+
    geom_point(size=1)+
    geom_line() +
    theme_minimal() +
    scale_x_discrete(limits = paste0(rep("PC", 20), 1:20)) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
          axis.text = element_text(size = 5),
          axis.title = element_text(size = 7)) +
    xlab("Principal Components (PC)") +
    ylab("Variance explained")
```

@@

data_pca <- data_pca[,1:7]
UMAP_fit_pbmc <- umap(data_pca, n_neighbors = 15, n_components =  2)

UMAP_data_pbmc <- UMAP_fit_pbmc$layout |>
  as.data.frame()

names(UMAP_data_pbmc)[1:(ncol(UMAP_data_pbmc))] <- paste0(rep("UMAP",(ncol(UMAP_data_pbmc))), 1:(ncol(UMAP_data_pbmc)))

UMAP_data_pbmc <- UMAP_data_pbmc |>
  mutate(ID = row_number())

plot_pbmc <- UMAP_data_pbmc %>%
    ggplot(aes(x = UMAP1,
               y = UMAP2, color = data_pca_with_label$cluster_label))+
    geom_point(alpha=0.5) +
    coord_equal() +
    theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
    theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
              axis.title.x = element_blank(), axis.title.y = element_blank(),
              axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_blank(), axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
         legend.key.height = unit(0.25, 'cm'),
         legend.key.width = unit(0.25, 'cm')) +
  scale_color_manual(values=c("#b15928", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#6a3d9a", "#ff7f00", "#cab2d6", "#fdbf6f", "#ffff99", "#a6cee3", "#8dd3c7", "#ffffb3", "#bebada", "#fb8072", "#80b1d3", "#fdb462", "#b3de69", "#fccde5", "#d9d9d9", "#bc80bd", "#ccebc5", "#ffed6f", "#000000", "#bdbdbd")) +
  guides(color = guide_legend(title = "Cell type"),
         color = guide_legend(nrow = 3))
```

```{r}
#| echo: false
cell_area <- 1

num_bins_pbmc <- calculate_effective_x_bins(.data = UMAP_data_pbmc, x = UMAP1,
                                        cell_area = 1)
shape_val_pbmc <- calculate_effective_shape_value(.data = UMAP_data_pbmc,
                                              x = UMAP1, y = UMAP2)

## To extract bin centroids
hexbin_data_object_pbmc <- extract_hexbin_centroids(nldr_df = UMAP_data_pbmc, num_bins = num_bins_pbmc, shape_val = shape_val_pbmc)

df_bin_centroids_pbmc <- hexbin_data_object_pbmc$hexdf_data

UMAP_data_with_hb_id_pbmc <- UMAP_data_pbmc |> 
  dplyr::mutate(hb_id = hexbin_data_object_pbmc$hb_data@cID)

## To generate a data set with high-D and 2D training data
data_pca_n <- data_pca
names(data_pca_n) <- paste0(rep("x", 7), 1:7)
df_all_pbmc <- dplyr::bind_cols(data_pca_n, UMAP_data_with_hb_id_pbmc)

## Averaged on high-D
df_bin_pbmc <- avg_highD_data(.data = df_all_pbmc)

## Triangulate bin centroids
tr1_object_pbmc <- triangulate_bin_centroids(df_bin_centroids_pbmc, x, y)
tr_from_to_df_pbmc <- generate_edge_info(triangular_object = tr1_object_pbmc)

## Compute 2D distances
distance_pbmc <- cal_2D_dist(.data = tr_from_to_df_pbmc)

## To find the benchmark value
benchmark_pbmc <- find_benchmark_value(.data = distance_pbmc, distance_col = distance)

benchmark_pbmc <- 2

names(df_all_pbmc)[1:7] <- paste0(rep("PC_", 7), 1:7)
names(df_bin_pbmc) <- c("hb_id", paste0(rep("PC_", 7), 1:7))

# tour_pbmc <- show_langevitour(df_all_pbmc, df_bin_pbmc, df_bin_centroids_pbmc, benchmark_value = benchmark_pbmc, distance = distance_pbmc, distance_col = distance, col_start = "PC")

df_1 <- df_all_pbmc |> 
  dplyr::select(tidyselect::starts_with("PC")) |>
  dplyr::mutate(type = data_pca_with_label$cluster_label) ## original dataset

df_b_1 <- df_bin_pbmc |> 
  dplyr::filter(hb_id %in% df_bin_centroids_pbmc$hexID) |>
  dplyr::select(-hb_id) |>
  dplyr::mutate(type = "model") ## Data with summarized mean

df_exe <- dplyr::bind_rows(df_b_1, df_1)

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_pbmc %>% 
  dplyr::filter(distance < benchmark_pbmc)
## Since erase brushing is considerd.

trimesh_pbmc <- ggplot(df_bin_centroids_pbmc, aes(x = x, y = y)) +
  geom_trimesh() +
  coord_equal()

trimesh_pbmc <- trimesh_pbmc +
  #ggtitle("(b)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme(axis.text = element_text(size = 5),
          axis.title = element_text(size = 7))

trimesh_gr_pbmc <- colour_long_edges(.data = distance_pbmc, benchmark_value = benchmark_pbmc,
                 triangular_object = tr1_object_pbmc, distance_col = distance)

trimesh_gr_pbmc <- trimesh_gr_pbmc +
  #ggtitle("(c)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme(axis.text = element_text(size = 5),
          axis.title = element_text(size = 7), #change legend key width
        legend.title = element_text(size=7), #change legend title font size
        legend.text = element_text(size=5))

tour_pbmc <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)], lineFrom = distance_df_small_edges$from, lineTo = distance_df_small_edges$to, group = df_exe$type, levelColors = c("#33a02c", "#b2df8a", "#fb9a99", "#ff7f00", "#e31a1c", "#1f78b4", "black", "#b15928", "#6a3d9a", "#cab2d6"), pointSize = 3)
```

```{r}
#| warning: false
#| echo: false
#| out-width: 100%
#| label: fig-pbmc
#| fig-pos: H
#| fig-cap: Visualization and refinement of low-dimensional representation for pbmc data$\colon$ (a) 2D layout of UMAP (n-neigbors = 15), (b) triangular mesh, and (c) triangular mesh colored by edge type. Edges with lengths less than the benchmark value of $2$ are classified as small, while edges with lengths greater than or equal to this value are labeled as long. The combination of UMAP, hexagonal binning, and triangulation provides the effectiveness of our approach in visualizing and refining the low-dimensional representation of the pbmc data.

plot_pbmc + trimesh_pbmc + trimesh_gr_pbmc + #A = 1, b = (19, 27), s = 1.255103
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect') &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

<!--
::: {#fig-pbmc_sc layout-ncol="3"}
![](figures/pbmc_a.png){#fig-pbmc_sc1}

![](figures/pbmc_b.png){#fig-pbmc_sc2}

![](figures/pbmc_c.png){#fig-pbmc_sc3}

Screen shots of the **langevitour** with the low-dimensional view applied to pbmc data set, a video of the tour animation is available at (\url{https://drive.google.com/file/d/1F7Xb2EIpfUruCxYihPw2rKro4FB5Y2uL/view}). Combination of the **langevitour** and low-dimensional representation of the pbmc data provides the effectiveness of our approach.
:::-->

@@

>>>>

a2 + a1 +
  plot_annotation(tag_levels = 'a') +
  plot_layout(ncol = 3) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```

@@

## To draw with AIC
aic_plot_param <- ggplot(MSE_df_umap |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                                                                         y = total_error,
                                                                         color = param
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(legend.title = element_blank(), legend.text = element_text(size=7), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_color_discrete_qualitative() +
  ylab("AIC") +
  xlab("Total number of bins")
## Effective number of bins along x-axis

mse_plot_param_training <- ggplot(MSE_df_umap |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                               y = total_mse,
                               color = param
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.title = element_blank(), legend.text = element_text(size=7), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_color_discrete_qualitative() +
  ylab("MSE") +
  xlab("Total number of bins")

mse_plot_param_test <- ggplot(MSE_df_umap |> dplyr::filter(data_type == "test"), aes(x = number_of_bins,
                                                                                             y = total_mse,
                                                                                             color = param
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(legend.title = element_blank(), legend.text = element_text(size=7), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_color_discrete_qualitative() +
  ylab("MSE") +
  xlab("Total number of bins")

@@

@@

## Import data
df_2 <- read_rds("data/pbmc/pbmc.rds")
training_data_1 <- read_rds("data/pbmc/pbmc_training.rds")
test_1 <- read_rds("data/pbmc/pbmc_test.rds")

tSNE_pbmc <- read_rds("data/pbmc/pbmc_tsne_30.rds")
UMAP_pbmc <- read_rds("data/pbmc/pbmc_umap.rds")
PHATE_pbmc <- read_rds("data/pbmc/pbmc_phate.rds")
TriMAP_pbmc <- read_rds("data/pbmc/pbmc_trimap.rds")
PaCMAP_pbmc <- read_rds("data/pbmc/pbmc_pacmap.rds")

plot_list1_pbmc <- plot_tSNE_2D(tSNE_pbmc) + #ggtitle("(a)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'a', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

plot_list2_pbmc <- plot_UMAP_2D(UMAP_pbmc) + #ggtitle("(b)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'b', x = Inf, y = Inf, hjust = 1.5, vjust = 1.5, size = 3)

plot_list3_pbmc <- plot_PHATE_2D(PHATE_pbmc) + #ggtitle("(c)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'c', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

plot_list4_pbmc <- plot_TriMAP_2D(TriMAP_pbmc) + #ggtitle("(d)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'd', x = Inf, y = Inf, hjust = 1.5, vjust = 1.5, size = 3)

plot_list5_pbmc <- plot_PaCMAP_2D(PaCMAP_pbmc) + #ggtitle("(e)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'e', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)
```

```{r}
#| echo: false
#| fig-cap: "2D layouts from different NLDR techniques applied for the training PBMC dataset: (a) tSNE (perplexity = 30), (b) UMAP (n_neighbors = 15), (c) PHATE (knn = 5), (d) TriMAP (n_inliers = 5, n_outliers = 4, n_random = 3), and (e) PaCMAP (n_neighbors = 10, init = random, MN_ratio = 0.9, FP_ratio = 2). Is there a best representation of the original data or are they all providing  equivalent information?"
#| label: fig-nldervis5PBMC
#| out-width: 100%

plot_list1_pbmc + plot_list2_pbmc + plot_list3_pbmc + plot_list4_pbmc + plot_list5_pbmc +
  plot_layout(ncol=5)
```

@@

## Import data
df_2 <- read_rds("data/zeisel/zeisel.rds")
training_data_1 <- read_rds("data/zeisel/zeisel_training.rds")
test_1 <- read_rds("data/zeisel/zeisel_test.rds")

tSNE_zeisel <- read_rds("data/zeisel/zeisel_tsne_30.rds")
UMAP_zeisel <- read_rds("data/zeisel/zeisel_umap.rds")
PHATE_zeisel <- read_rds("data/zeisel/zeisel_phate.rds")
TriMAP_zeisel <- read_rds("data/zeisel/zeisel_trimap.rds")
PaCMAP_zeisel <- read_rds("data/zeisel/zeisel_pacmap.rds")

plot_list1_zeisel <- plot_tSNE_2D(tSNE_zeisel) + #ggtitle("(a)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'a', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

plot_list2_zeisel <- plot_UMAP_2D(UMAP_zeisel) + #ggtitle("(b)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'b', x = Inf, y = Inf, hjust = 1.5, vjust = 1.5, size = 3)

plot_list3_zeisel <- plot_PHATE_2D(PHATE_zeisel) + #ggtitle("(c)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'c', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

plot_list4_zeisel <- plot_TriMAP_2D(TriMAP_zeisel) + #ggtitle("(d)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'd', x = Inf, y = Inf, hjust = 1.5, vjust = 1.5, size = 3)

plot_list5_zeisel <- plot_PaCMAP_2D(PaCMAP_zeisel) + #ggtitle("(e)") + 
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'e', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)
```

```{r}
#| echo: false
#| fig-cap: "2D layouts from different NLDR techniques applied for the training Zeisel mouse brain dataset: (a) tSNE (perplexity = 30), (b) UMAP (n_neighbors = 15), (c) PHATE (knn = 5), (d) TriMAP (n_inliers = 5, n_outliers = 4, n_random = 3), and (e) PaCMAP (n_neighbors = 10, init = random, MN_ratio = 0.9, FP_ratio = 2). Is there a best representation of the original data or are they all providing  equivalent information?"
#| label: fig-nldervis5Mouse
#| out-width: 100%

plot_list1_zeisel + plot_list2_zeisel + plot_list3_zeisel + plot_list4_zeisel + plot_list5_zeisel +
  plot_layout(ncol=5)
```

### 2024-01-10 paper.tex
Add 2D layouts of PBMC and Mouse data

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, boxrule=0pt, frame hidden, enhanced, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

Next, we employed the UMAP technique with default parameter settings. As
illustrated in Figure~\ref{fig-pbmc}, the cell types B and Platelet are
well-separated in the UMAP layout. Moreover, CD14+ Mono, FCGR3A+ Mono,
and DC form a distinct cluster, while Naive CD4 T, NK, Memory CD4 T, and
CD8 T are grouped together in another cluster. The values utilized to
construct the smooth low-dimensional manifold are presented in
\textbf{?@tbl-table02}. The linked video, demonstrating the tour with
the model, showcases the generation of a smooth surface for this
application, enabling a comprehensive exploration of the data's
structure and relationships (see \textbf{?@fig-pbmc\_sc}).

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-pbmc-1.pdf}

@@

\caption{\label{fig-pbmc}Visualization and refinement of low-dimensional
representation for pbmc data\(\colon\) (a) 2D layout of UMAP (n-neigbors
= 15), (b) triangular mesh, and (c) triangular mesh colored by edge
type. Edges with lengths less than the benchmark value of \(2\) are
classified as small, while edges with lengths greater than or equal to
this value are labeled as long. The combination of UMAP, hexagonal
binning, and triangulation provides the effectiveness of our approach in
visualizing and refining the low-dimensional representation of the pbmc
data.}

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced]}{\end{tcolorbox}}\fi

@@

Next, we employed the UMAP technique with default parameter settings. As
illustrated in \textbf{?@fig-pbmc}, the cell types B and Platelet are
well-separated in the UMAP layout. Moreover, CD14+ Mono, FCGR3A+ Mono,
and DC form a distinct cluster, while Naive CD4 T, NK, Memory CD4 T, and
CD8 T are grouped together in another cluster. The values utilized to
construct the smooth low-dimensional manifold are presented in
\textbf{?@tbl-table02}. The linked video, demonstrating the tour with
the model, showcases the generation of a smooth surface for this
application, enabling a comprehensive exploration of the data's
structure and relationships (see \textbf{?@fig-pbmc\_sc}).

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-nldervis5PBMC-1.pdf}

@@

\caption{\label{fig-nldervis5PBMC}2D layouts from different NLDR
techniques applied for the training PBMC dataset: (a) tSNE (perplexity =
30), (b) UMAP (n\_neighbors = 15), (c) PHATE (knn = 5), (d) TriMAP
(n\_inliers = 5, n\_outliers = 4, n\_random = 3), and (e) PaCMAP
(n\_neighbors = 10, init = random, MN\_ratio = 0.9, FP\_ratio = 2). Is
there a best representation of the original data or are they all
providing equivalent information?}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-nldervis5Mouse-1.pdf}

\caption{\label{fig-nldervis5Mouse}2D layouts from different NLDR
techniques applied for the training Zeisel mouse brain dataset: (a) tSNE
(perplexity = 30), (b) UMAP (n\_neighbors = 15), (c) PHATE (knn = 5),
(d) TriMAP (n\_inliers = 5, n\_outliers = 4, n\_random = 3), and (e)
PaCMAP (n\_neighbors = 10, init = random, MN\_ratio = 0.9, FP\_ratio =
2). Is there a best representation of the original data or are they all
providing equivalent information?}
